\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Rev 1\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

\section{Revision 1 Plans}

The team's main focus goals leading up to the final revision was to finalize tuning on our AI models for eRisk Submission, create necessary assets for the EXPO (Poster and Video), and finalize Documentation.

\section{Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 13\\
Benjamin Chinnery & 10\\
Micheal Breau & 13\\
Jessica Dawson & 13\\
Matthew Curtis & 12\\
Yaruo Tian & 11\\
\bottomrule
\end{tabular}
\end{table}
Overall, there were minimal discrepancies between group members in terms of meeting attendance since the Rev 0 Demo. Absences between meetings were always cleared by the team and given in advance so that other group members could gather the necessary information and stay on schedule. Absences were never given without a valid reason, whether it be because of course conflicts, sickness, or McMaster club involvement such as the Mac Eng Musical or Concrete Toboggan.

Additional meetings outside of the core functionality are not mandated for all members to attend, as they may consist of ops team integration, or may be more task specific on topics not associated with that specific member. Teammates which cannot attend these non-mandatory briefings are allowed to devote that time however they wish, as will be briefed on any developments at the next core team meeting.


\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Benjamin Chinnery & 0\\
Michael Breau & 1\\
Jessica Dawson & 0\\
Matthew Curtis & 0\\
Yaruo Tian & 0\\
\bottomrule
\end{tabular}
\end{table}

Since Rev 0, there has only been 1 lecture, and many teammates were unable to attend that day due to a variety of circumstances. 2 teammates were sick that day, and 2 others had midterms later that day that they needed to focus on, luckily we still had 1 teammate that was able to attend and pass on information for the rest of the group. Members who were unable to attend were instructed to read through the corresponding lecture slides 

\section{Commits}

This data represents the number of commits to both the Document Repository and the Private Code Repository since the POC demonstation. 
\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 36 & 100\% \\
Benjamin Chinnery & 6 & 16.7\%\\
Michael Breau & 9 & 25\%\\
Jessica Dawson & 11 & 30.5\%\\
Matthew Curtis & 1 & 2.8\%\\
Yaruo Tian & 9 & 25\%\\
\bottomrule
\end{tabular}
\end{table}

The data displayed above would tend to illustrate a rather uneven distribution of work amongst team members, but luckily team members have been satisfied with the overall distribution of effort, and these unequal commit numbers boil down to variations within assigned tasks, associated teamwork per task, as well as individual's committing approach. To elaborate on this, team members working a joint task may find themselves needing to commit more frequently to keep branches up to date, rather than members working on individual assignments. Additionally, the number of tasks can be directly corresponding to the type of task itself, for example Michael's work on the continuous integration Pylint checkers required numerous commits to main in order to test functionality.

Finally, certain efforts from team members may not be sufficiently displayed, if they were spending their time experimenting with methodologies that would not end up being merged into main, as well as if they were updating documentation intended for internal stakeholder and supervisor use on the UQAM overleaf repository, as those private documents are not intended to be pushed to main or shared.



\section{Issue Tracker}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Benjamin Chinnery & 10 & 4 \\
Jessica Dawson& 9 & 2 \\
Matthew Curtis & 10 & 2 \\
Michael Breau & 15 & 9 \\
Yaruo Tian & 18 & 11 \\
\bottomrule
\end{tabular}
\end{table}

These numbers are determined using the issue tracker's filter function.



\end{document}